### 2020-12-12 exploratory/2020-11/plots.Rmd
Weird pattern in incorrect fraction mapped results

>>>>

### is there a pattern?

```{r debug_frac_map}
debug_dat <- optifit_split %>% 
  filter(method == 'open') %>% 
  mutate(is_correct = fraction_mapped == 1) %>% 
  select(dataset, seed, method, fraction_mapped, is_correct, 
         sample_frac, ref_frac, ref_weight) %>%
  group_by(dataset, seed, ref_frac, ref_weight, is_correct)

debug_dat %>% filter(seed ==1, ref_weight == 'distance', dataset == 'soil') %>% pull(is_correct)
debug_dat %>% filter(seed ==2, ref_weight == 'distance', dataset == 'soil') %>% pull(is_correct)

debug_dat %>% filter(seed ==1, ref_weight == 'distance', dataset == 'human') %>% pull(is_correct)
debug_dat %>% filter(seed ==2, ref_weight == 'distance', dataset == 'human') %>% pull(is_correct)

```

## diversity
